Automated Formal Synthesis\\ of Safe Digital Controllers for Continuous Plants

### 2019-01-08 automatica/paper.tex
grammar

We consider models of physical plants expressed as ordinary differential
equations, which we assume to be controllable~\cite{Astrom08}: 
%
\begin{align}
\label{eq:ode1}
\dot{x}(t) = \mat{A}\vec{x}(t)+ \mat{B} \vec{u}(t), 
\end{align}
%
where 
$\vec{x} \in \mathbb{R}^p$,  
$\vec{u} \in \mathbb{R}^q$, 
$\mat{A} \in \mathbb{R}^{p \times p}$, 
$\mat{B} \in \mathbb{R}^{p \times q}$,
and $t \in \mathbb R_0^+$ denotes continuous time. 
%$\mat{A}$ and $\mat{B}$ are matrices that fully characterize the dynamics of the continuous plant,
We denote with $x(0)$ the initial state of the model.

@@

We account for the presence of errors originating from a number of sources, shown in Figure~\ref{fig:digitalsystem}:
\begin{itemize}
\item We represent the plant variables $x(t)$ and $u(t)$, which are continuous quantities, with finite precision in our model. 
It is necessary to account for the errors introduced by this representation, 
which we do using standard interval arithmetic. 
\item The quantisation errors by the ADC, which converts the analogue signal $x(t)$ into the digital signal $x_k$, 
which is then fed into the controller cf. Figure~\ref{fig:digitalsystem}. 
\ifx\axelerator
We account for this error in the acceleration-based back-end by introducing a noise signal $\nu_1$ that over-approximates it. 
Further details are found in Section~\ref{sssec:abstraction}.  
In the multi-stage back-end we
\else
We
\fi
use bit-precise modelling in CBMC~\cite{ClarkeKL04}, a bounded model checker for C-programs, to accurately encompass this conversion. 
In other words, CBMC constructs a Boolean formula that explicitly unwinds the transition system for symbolically represented initial states. 
The values that the symbolically represented initial state may take are restricted by upper and lower bounds as described in section~\ref{}.
The Boolean formula constructed by CBMC models the ADC conversions precisely on the symbolically represented states at every time step. 
When we check for a safety property, the Boolean formula is satisfied only if there is an input state value for which the subsequent trace through the transition system eventually violates the safety property.

>>>>

We consider models of physical plants expressed as ordinary differential
equations, which we assume are controllable~\cite{Astrom08}: 
%
\begin{align}
\label{eq:ode1}
\dot{x}(t) = \mat{A}\vec{x}(t)+ \mat{B} \vec{u}(t), 
\end{align}
%
where 
$\vec{x} \in \mathbb{R}^p$,  
$\vec{u} \in \mathbb{R}^q$, 
$\mat{A} \in \mathbb{R}^{p \times p}$, 
$\mat{B} \in \mathbb{R}^{p \times q}$,
and $t \in \mathbb R_0^+$ denotes continuous time. 
%$\mat{A}$ and $\mat{B}$ are matrices that fully characterize the dynamics of the continuous plant,
We denote with $x(0)$ the initial state of the model.

@@

We account for the presence of errors originating from a number of sources, shown in Figure~\ref{fig:digitalsystem}:
\begin{itemize}
\item We represent the plant variables $x(t)$ and $u(t)$, which are continuous quantities, with finite precision in our model. 
which we do using standard interval arithmetic. 
\item The quantisation errors by the ADC, which converts the analogue signal $x(t)$ into the digital signal $x_k$, 
which is then fed into the controller cf. Figure~\ref{fig:digitalsystem}. 
\ifx\axelerator
We account for this error in the acceleration-based back-end by introducing a noise signal $\nu_1$ that over-approximates it. 
Further details are found in Section~\ref{sssec:abstraction}.  
In the multi-stage back-end we
\else
We
\fi
use bit-precise modelling in CBMC~\cite{ClarkeKL04}, a bounded model checker for C-programs, to accurately encompass this conversion. 
In other words, CBMC constructs a Boolean formula that explicitly unwinds the transition system for symbolically represented initial states. 
The values that the symbolically represented initial state may take are restricted by upper and lower bounds as described in section~\ref{}.
The Boolean formula constructed by CBMC models the ADC conversions precisely on the symbolically represented states at every time step. 
When we check for a safety property, the Boolean formula is satisfied only if there is an input state value for which the subsequent trace through the transition system eventually violates the safety property.
